%%%%%%%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your contribution to a "contributed book"
%
% "contributed book"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%


% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{svmult}

% choose options for [] as required from the list
% in the Reference Guide, Sect. 2.2

\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
% etc.
% see the list of further useful packages
% in the Reference Guide, Sects. 2.3, 3.1-3.3

\makeindex             % used for the subject index
                       % please use the style sprmidx.sty with
                       % your makeindex program


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{cleveref}
\include{vehmacros}
\begin{document}

\title*{Automated Edge Grid Generation Based on Arc-Length Optimization}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{David McLaurin\inst{1}\and
Suzanne M. Shontz\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{High Performance Computing Collaboratory,
           Center for Advanced Vehicular Systems,
	       Graduate Program in Computational Engineering,
		   Mississippi State University, Mississippi State, MS, 
U.S.A.,
		   \texttt{d.mclaurin@msstate.edu}
\and Department of Mathematics and Statistics,
     Department of Computer Science and Engineering,
	 Center for Computational Sciences,
	 Graduate Program in Computational Engineering,
	 Mississippi State University, Mississippi State, MS, U.S.A.,
     \texttt{sshontz@math.msstate.edu} }
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

%% main text
\begin{abstract}
Computational design and analysis has become a fundamental part of 
industry and academia for use in research, development, and manufacturing.  
In general, the accuracy of a computational analysis depends heavily on 
the fidelity of the computational representation of a real-world object or 
phenomenon. Most mesh generation strategies focus on element quality--with 
the justification being that downstream applications require high quality 
geometries in order to achieve a desired level of accuracy. However, 
element quality should be secondary to accurately representing the 
underlying physical object or phenomenon.  This work seeks to improve the 
process of creating a computational model of an object of interest by 
accelerating the process of mesh generation by reducing the need for 
(often) manual intervention. This acceleration will be accomplished by 
automatically generating \textit{optimal} discretizations of curves by 
minimizing the \textit{arc-length deficit}.  We propose a method for
generating optimal discretizations through local optimization of the 
arclength.  Our results demonstrate the robustness and accuracy of
our optimal discretization technique.  We also discuss how to incorporate 
our edge grid generator into existing mesh generation software.
\keywords{mesh, grid, adaptive, refinement, optimal, edge}
\end{abstract}

\input{Introduction}

\input{Related_Work}

\input{Discretization_Error}

\input{Discrete_Curvature_Approximation}

\input{Refinement_via_Arc-Length_Deficit}

\input{Error_Bounds}

\input{Element_Quality}

\input{Results}

\input{Conclusions}

\input{Acknowledgments}

%
%
% BibTeX users please use
\bibliographystyle{ieeetr}
\bibliography{References}
%
% Non-BibTeX users please follow the syntax
% the syntax of "referenc.tex" for your own citations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\printindex
\end{document}





